Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-07-21 Report/convergence_centralized.tex
finalized

To solve \eqref{con}, we adopt \ac{AO} by fixing a block of variables and optimize for others \cite{bezdek2002some}. In \eqref{con}, even after fixing the variable \me{\my}, the problem is still nonconvex due to the constraint \eqref{con-dc}. To overcome this issue, we resort to \ac{SCA} principle presented in \cite{lanckriet2009convergence,scutari_1,yang_yang} by relaxing the nonconvex set by a sequence of convex subsets. Since it involves two nested iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{SCA} step by a subscript \me{k}. Let \me{\iter{\mx}{\ast}{i}} be the value of \me{\mx} when the \ac{SCA} iteration converges in the \me{\ith{i}} \ac{AO} iteration and let \me{\iter{\mz}{\ast|\my}{i}} be the solution for \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iteration for a fixed \me{\my}. Let \eqn{\mx_k^{(i)}} denotes the stacked transmit precoders of all users at the \eqn{\ith{k}} \ac{SCA} step in the \eqn{\ith{i}} \ac{AO} iteration.

@@

\review{To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + \frac{c}{2} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c > 0} is a positive constant to ensure strong convexity in the objective, and therefore guarantees the unique minimizer \cite{yang_yang}. Note that the quadratic term in \eqref{mod_obj} includes the previous solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, which is solved in the \eqn{\ith{k}} \ac{SCA} iteration.}

@@

Thus the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing. \review{Since the objective is strongly convex due to the introduced quadratic term in \eqref{mod_obj}, the minimizer \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}\}} in each \ac{SCA} step is unique. Using this and the fact that the sequence of objectives is nondecreasing ensure that the iterates of the \ac{SCA} update converges to a limit point in the \eqn{\ith{i}} \ac{AO} step.  However, note that the limit point need not be a stationary point of \eqref{con} since the receive beamformers \eqn{\my} have been fixed.}

@@

Once the solution is found for a fixed \me{\my}, it is then optimized by fixing \me{\mx} as \me{\iter{\mx}{\ast}{i}}. Even after treating \me{\mx} as a constant, the problem is nonconvex due to the \ac{DC} constraint. Following similar approach as above, we can find a minimizer \me{ \{\iter{\mx}{\ast}{i},\iter{\my}{k+1}{i},\iter{\mz}{k+1}{i}\}} for a similar convex subproblem \eqref{con-m} at each iteration \me{{k}}. Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration. The convergence and the nonincreasing behavior of the objective follow similar arguments as above.\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The limit point of the converged \ac{SCA} subproblems with \me{\my} as a variable is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}}, which is the minimizer in the feasible set \me{\iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.

Finally, to prove the global convergence of the iterative algorithm, we need to show the \ac{AO} updates also produce a nondecreasing sequence of objectives, \textit{i.e.}, 
\iftoggle{single_column}{
\begin{equation}
f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
\end{equation}}{
\begin{equation}
f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
\end{equation}}
Let \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mz}{\ast|\my}{i}} be the solution obtained by solving \eqref{con-m} iteratively until \ac{SCA} convergence in the \me{\ith{i}} \ac{AO} iteration for \eqn{\mx} and \eqn{\mz} with fixed \eqn{\my = \iter{\my}{\ast}{i-1}}. To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}. Since the convex function is linearized in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \iter{\mc{Y}}{0}{i}} by the equality in \eqref{con-sub-set}. Using this, we can show the monotonicity of the objective as
\begin{equation} \label{fixed_point}
f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\mx}{i}).
\end{equation}
The \ac{AO} update follows \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}.

\review{Note that the \ac{AO} and \ac{SCA} iterative procedures generates a nonincreasing sequence of objectives for the original function in \eqref{orig_obj} using the above discussions. However, by using the regularized objective in \eqref{mod_obj}, we can show that the sequence of objectives provided by \ac{AO} and \ac{SCA} steps is strictly increasing. Let \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} be the solution of \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step. In order to show the strict monotonicity of the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} method, we rely on the strong convexity of \eqref{mod_obj}. %We know that the objective decreases in each \ac{SCA} step, since the \eqn{\ith{(k-1)}} solution \eqn{\mbf{z}^{(i)}_{k}} is a feasible point of \eqn{\mc{X}_{k}^{(i)}} in the \eqn{\ith{k}} \ac{SCA} step \cite{marks1978technical}. 
It follows by the strong convexity of \eqref{mod_obj} with \eqn{m > 0} in the \eqn{\ith{k}} update
\begin{equation} \label{strict_monotonicity}
f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) \geq \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}) + m \, \|\mbf{z}_{k+1}^{(i)} - \iter{\mbf{z}}{k}{i}\|^2  \eqspace
\end{equation}
since \eqn{\iter{\mbf{z}}{k+1}{i}} is the minimizer of \eqref{con-m}. Note that \eqref{strict_monotonicity} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}} as \eqn{k \rightarrow \infty}. Using the facts that (i) the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} approach is monotonic \cite{marks1978technical}, and  (ii) the uniqueness of the minimizer in each \ac{SCA} step (see \eqref{strict_monotonicity}), we can ensure the strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}}. However, if \eqn{\hat{f}} is used as the objective in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to the existence of multiple solutions.

Similarly, we can also guarantee strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update. Since \eqn{\iter{\mbf{z}}{\ast}{i}} is also included in the set \eqn{\mc{Y}_{0}^{i}}, the objective function follows \eqref{fixed_point} strictly unless the overall sequence \eqn{\{\mbf{z}_{\ast}^{i} \}} converges to a limit point as \eqn{i \rightarrow \infty}.}

@@

@@

\subsection{Convergence of the Beamformer Iterates} \label{c-b}
Let \me{\ma \triangleq [\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}]} be the stacked vector of the solution point from the \eqn{\ith{i}} \ac{AO} iteration and let \me{\mc{A}} be a point-to-set mapping algorithm defined as
\begin{equation} \label{g-algo}
\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i}) \triangleq
\begin{cases}
\underset{\mx,\mz}{\mathrm{argmin}} \; f(\mx,\mz;\iter{\my}{\ast}{i-1})& \forall \mx,\mz \in \iter{\mc{X}}{\ast}{i} \\
\underset{\my,\mz}{\mathrm{argmin}} \; f(\my,\mz;\iter{\mx}{\ast}{i})& \forall \my,\mz \in \iter{\mc{Y}}{\ast}{i} 
\end{cases} 
\end{equation}
Note that in each iteration \me{i}, the algorithm \eqn{\mc{A}} in \eqref{g-algo} includes two \ac{SCA} updates performed until convergence, \textit{i.e.}, one for variable \me{\mx} and \me{\mz} by keeping \me{\my} fixed and another for \me{\my} and \me{\mz} by fixing \me{\mx} as constant. Since the minimizer is unique, the mapping can be defined as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})}. In order to prove the convergence of the beamformer iterates, we define \me{\mc{F}^\ast \subset \mc{F}} as the set of fixed points, \textit{i.e.}, \me{\forall {\ma}^{\ast} \in \mc{F}^\ast, \, {\ma}^{\ast} = \mc{A}({\ma}^{\ast})}, identified by the algorithm \me{\mc{A}} for different initialization points.

@@

Now, to prove the feasibility of the limit point \me{\ma^{\ast}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}. Therefore, the limit point \eqn{\ma^{\ast} \in \mc{F}} and it satisfies the Slater's constraint qualifications. Moreover, as discussed in Appendix \ref{c-b}, \eqn{\ma^{\ast}} is a regular point of the algorithm \eqn{\mc{A}} and also the solution for \eqref{con-m}, therefore, there exist Lagrange multipliers \eqn{\mu_i} such that
\begin{equation} \label{kkt_mod_expr}
\textstyle	\nabla f(\ma^{\ast}) + \mu_0 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast};\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0.
\end{equation}
The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \rightarrow \infty, \ma^{(i)} \rightarrow \ma^{\ast}}, since \eqn{\ma^{\ast}} is the fixed point of \eqn{\mc{A}}. Therefore, the gradients evaluated at \eqn{\ma^{\ast}} satisfies \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})}. (ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the \ac{DC} constraint \eqref{con-dc} evaluated at \eqn{\ma^{\ast}} is given by
\begin{equation} \label{rhs_equiv}
\nabla h(\ma^{\ast}) - \nabla \hat{g}_o(\mbf{\ma}^{\ast};\mbf{\ma}^{\ast}) = \nabla h(\ma^{\ast}) - \nabla g_o(\mbf{\ma}^{\ast}).
\end{equation}
Now, by applying the relation in \eqref{rhs_equiv} and \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\ma^{\ast}} satisfies \eqref{kkt_expr}. By using \cite[Th. 2 and 11]{scutari_1} or \cite[Prop. 3.2]{amir}, we can show that the limit point of the sequence \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} is a stationary point of \eqref{con}.}

>>>>

To solve \eqref{con}, we adopt \ac{AO} by fixing a block of variables and optimize for others \cite{bezdek2002some}. In \eqref{con}, even after fixing the variable \me{\my}, the problem is still nonconvex due to the constraint \eqref{con-dc}. To overcome this issue, we resort to \ac{SCA} principle presented in \cite{lanckriet2009convergence,scutari_1,yang_yang} by relaxing the nonconvex set by a sequence of convex subsets. Since it involves two nested iterations, we denote the \ac{AO} step index by a superscript \me{(i)} and the \ac{SCA} iteration by a subscript \me{k}. Let \me{\iter{\mx}{\ast}{i}} be the value of \me{\mx} when the \ac{SCA} iteration converges in the \me{\ith{i}} \ac{AO} iteration and let \me{\iter{\mz}{\ast|\my}{i}} be the solution for \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iteration for a fixed \me{\my}. Let \eqn{\mx_k^{(i)}} denotes the stacked transmit precoders of all users at the \eqn{\ith{k}} \ac{SCA} step in the \eqn{\ith{i}} \ac{AO} iteration.

@@

\review{To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + \tfrac{c}{2} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c > 0} is a positive constant to ensure strong convexity in the objective, and therefore guarantees the unique minimizer \cite{yang_yang}. Note that the quadratic term in \eqref{mod_obj} includes the previous solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, which is solved in the \eqn{\ith{k}} \ac{SCA} iteration.}

@@

Thus the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing. \review{Since the objective is strongly convex due to the introduced quadratic term in \eqref{mod_obj}, the minimizer \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}\}} in each \ac{SCA} step is unique. Using this and the fact that the sequence of objectives is nonincreasing ensure that the iterates of the \ac{SCA} update converges to a limit point in the \eqn{\ith{i}} \ac{AO} step.  However, note that the limit point need not be a stationary point of \eqref{con} since the receive beamformers \eqn{\my} have been fixed.}

@@

Once \me{\iter{\mx}{\ast}{i}} is found for fixed \me{\my}, then \eqref{con} is solved for \me{\my} with fixed \me{\mx}. However, after fixing \me{\mx} as \me{\iter{\mx}{\ast}{i}} in \eqref{con}, the problem is still nonconvex due to \eqref{con-dc}. Following similar approach as above, the minimizer \me{ \{\iter{\mx}{\ast}{i},\iter{\my}{k+1}{i},\iter{\mz}{k+1}{i}\}} can be found in each \ac{SCA} step \me{k} by solving \eqref{con-m} iteratively. Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration. The sequence convergence and the nonincreasing behavior of the objective follow similar arguments as above.\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The limit point of the sequence of iterates generated by iteratively solving \eqref{con-m} is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\} \in \iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.

Finally, to prove the global convergence of the iterative algorithm, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
\iftoggle{single_column}{
\begin{equation}
f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
\end{equation}}{
\begin{equation}
f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
\end{equation}}
Let \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mz}{\ast|\my}{i}} be the solution obtained by solving \eqref{con-m} iteratively until \ac{SCA} convergence in the \me{\ith{i}} \ac{AO} iteration for \eqn{\mx} and \eqn{\mz} with fixed \eqn{\my = \iter{\my}{\ast}{i-1}}. To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}. Since the convex function is linearized in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \iter{\mc{Y}}{0}{i}} by the equality in \eqref{con-sub-set}. Using this, we can show the monotonicity of the objective as
\begin{equation} \label{fixed_point}
f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\mx}{i}).
\end{equation}
The \ac{AO} update follows \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}.

\review{Using the above discussions, the monotonicity of the objective seqeunce is guaranteed in each \ac{AO} and \ac{SCA} updates. However, to ensure strict monotonicity, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some parameter \eqn{m > 0}. Now, to show strict monotonicity, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step. At the \eqn{\ith{k}} \ac{SCA} iteration, \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}, it follows
\begin{IEEEeqnarray}{rCl} \neqsub \label{strict_monotonicity}
\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z} - \iter{\mbf{z}}{k+1}{i}) &\geq& 0 \eqsub \\
f(\mbf{z}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& \tfrac{m}{2} \, \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2 \eqsub
\end{IEEEeqnarray}
since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds at each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}} as \eqn{k \rightarrow \infty}. Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic \cite{marks1978technical}, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured. However, if \eqn{\hat{f}} is used instead of \eqn{f} in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to multiple solutions.

Similarly, we can also guarantee strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update. It follows from that fact that \eqn{\iter{\mbf{z}}{\ast}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} iteration unless the sequence \eqn{\{\mbf{z}_{\ast}^{i}\}} converges to a limit point as \eqn{i \rightarrow \infty}.}

@@

\begin{equation} \label{strict_monotonicity}
f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) \geq \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}) + \frac{m}{2} \, \|\mbf{z}_{k+1}^{(i)} - \iter{\mbf{z}}{k}{i}\|^2  \eqspace
\end{equation}

Note that the \ac{AO} and \ac{SCA} procedures generate a nonincreasing sequence of objectives for the original objective in \eqref{orig_obj} using the above discussions. However, by using the regularized objective in \eqref{mod_obj}, we can show that the sequence of objectives provided by \ac{AO} and \ac{SCA} steps is strictly decreasing. Let \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} be the solution of \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} \ac{SCA} step. Note that the objective \eqref{con-obj-m} is strongly convex with some parameter \eqn{m > 0}, and therefore \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}
\begin{IEEEeqnarray}{l}
f(\mbf{z}) \geq f(\iter{\mbf{z}}{k+1}{i}) + \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z} - \iter{\mbf{z}}{k+1}{i}) + \tfrac{m}{2} \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2. \eqspace 
\end{IEEEeqnarray}
Since \eqn{\iter{\mbf{z}}{k+1}{i}} is the minimizer for \eqref{con-m} in the \eqn{\ith{k}} \ac{SCA} step, 
\begin{IEEEeqnarray}{rCl} \neqsub \label{s_ineq_g}
\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}) &\geq& 0, \quad \iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i} \eqsub \\
f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& \tfrac{m}{2} \, \|\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}\|^2. \eqsub \label{s_ineq}
\end{IEEEeqnarray}
Note that \eqref{s_ineq} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}} as \eqn{k \rightarrow \infty}. Using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic \cite{marks1978technical}, and (ii) the uniqueness of the minimizer (see \eqref{s_ineq_g}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured. However, if \eqn{\hat{f}} is used as the objective in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to the existence of multiple solutions.

	In order to show the strict monotonicity of the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} method, we rely on the strong convexity of \eqref{mod_obj} with parameter \eqn{m > 0} as %We know that the objective decreases in each \ac{SCA} step, since the \eqn{\ith{(k-1)}} solution \eqn{\mbf{z}^{(i)}_{k}} is a feasible point of \eqn{\mc{X}_{k}^{(i)}} in the \eqn{\ith{k}} \ac{SCA} step \cite{marks1978technical}. 
	%It follows by the strong convexity of \eqref{mod_obj} with \eqn{m > 0} in the \eqn{\ith{k}} update
	\begin{equation} \label{strict_monotonicity}
	f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) \geq \underbrace{\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i})}_{= 0} + \frac{m}{2} \, \|\mbf{z}_{k+1}^{(i)} - \iter{\mbf{z}}{k}{i}\|^2  \eqspace
	\end{equation}
	since \eqn{\iter{\mbf{z}}{k+1}{i}} is the minimizer of \eqref{con-m}. Note that \eqref{strict_monotonicity} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}} as \eqn{k \rightarrow \infty}. Using the facts that (i) the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} approach is monotonic \cite{marks1978technical}, and  (ii) the uniqueness of the minimizer in each \ac{SCA} step (see \eqref{strict_monotonicity}), we can ensure the strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}}. However, if \eqn{\hat{f}} is used as the objective in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to the existence of multiple solutions.

@@

\subsection{Convergence of the Beamformer Iterates} \label{c-b}
Let \me{\ma^{(i)} \triangleq [\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}]} be the stacked vector of the solution point from the \eqn{\ith{i}} \ac{AO} iteration and let \me{\mc{A}} be a point-to-set mapping algorithm defined as
\begin{equation} \label{g-algo}
\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i}) \triangleq
\begin{cases}
\underset{\mx,\mz}{\mathrm{argmin}} \; f(\mx,\mz;\iter{\my}{\ast}{i-1})& \forall \mx,\mz \in \iter{\mc{X}}{\ast}{i} \\
\underset{\my,\mz}{\mathrm{argmin}} \; f(\my,\mz;\iter{\mx}{\ast}{i})& \forall \my,\mz \in \iter{\mc{Y}}{\ast}{i} 
\end{cases} 
\end{equation}
Note that in each iteration \me{i}, the algorithm \eqn{\mc{A}} in \eqref{g-algo} includes two \ac{SCA} updates performed until convergence, \textit{i.e.}, one for variable \me{\mx} and \me{\mz} by keeping \me{\my} fixed and another for \me{\my} and \me{\mz} by fixing \me{\mx} as constant. Since the minimizer is unique, the mapping can be defined as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})}. In order to prove the convergence of the beamformer iterates, we define \me{\mc{F}^\ast \subset \mc{F}} as the set of fixed points, \textit{i.e.}, \me{\forall {\ma}^{\ast} \in \mc{F}^\ast, \, {\ma}^{\ast} = \mc{A}({\ma}^{\ast})}, identified by the algorithm \me{\mc{A}} for different initialization points.

@@

Now, to prove the feasibility of the limit point \me{\ma^{\ast}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}. Therefore, the limit point \eqn{\ma^{\ast} \in \mc{F}} and it satisfies the Slater's constraint qualifications. Moreover, as discussed in Appendix \ref{c-b}, \eqn{\ma^{\ast}} is a regular point of the algorithm \eqn{\mc{A}} and also the solution for \eqref{con-m}, therefore, there exist Lagrange multipliers \eqn{\mu_i} such that
\begin{equation} \label{kkt_mod_expr}
\textstyle	\nabla f(\ma^{\ast}) + \mu_0 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast};\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0.
\end{equation}
The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \rightarrow \infty, \ma^{(i)} \rightarrow \ma^{\ast}}, since \eqn{\ma^{\ast}} is the fixed point of \eqn{\mc{A}}. Therefore, the gradients evaluated at \eqn{\ma^{\ast}} satisfies \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})}. (ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the \ac{DC} constraint \eqref{con-dc} evaluated at \eqn{\ma^{\ast}} is given by
\begin{equation} \label{rhs_equiv}
\nabla h(\ma^{\ast}) - \nabla \hat{g}_o(\mbf{\ma}^{\ast};\mbf{\ma}^{\ast}) = \nabla h(\ma^{\ast}) - \nabla g_o(\mbf{\ma}^{\ast}).
\end{equation}
Now, by applying the relation in \eqref{rhs_equiv} and \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\ma^{\ast}} satisfies \eqref{kkt_expr}. By using \cite[Th. 2 and 11]{scutari_1} or \cite[Prop. 3.2]{amir}, we can show that the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} is a stationary point of the original nonconvex problem in \eqref{con}.}
